---
title: "Code Style"
author: Zachary del Rosario
date: 2020-05-05
output: github_document
time: 10
reading: 10
---

*Purpose*: From the tidyverse style guide "Good coding style is like correct
punctuation: you can manage without it, butitsuremakesthingseasiertoread." We
will follow the [tidyverse style guide](https://style.tidyverse.org/); Google's
internal [R style guide](https://google.github.io/styleguide/Rguide.html) is
actually based on these guidelines!

*Reading*: [tidyverse style guide](https://style.tidyverse.org/).
*Topics*: [Spacing](https://style.tidyverse.org/syntax.html#spacing) (subsection only), [Pipes](https://style.tidyverse.org/pipes.html) (whole section)
*Reading Time*: ~ 10 minutes

```{r setup}
library(tidyverse)
```

__q1__ Re-write according to the style guide

*Hint*: The pipe operator `%>%` will help make this code more readable.

```{r q1-task}
## Original code; hard to read
summarize(group_by(diamonds, cut), mean_price = mean(price))
```

```{r q1-solution}
## TODO: Re-write the code above following the tidyverse style guide
```

__q2__ Re-write according to the style guide

*Hint*: There are *particular rules* about spacing!

```{r q2-task}
## NOTE: You can copy this code to the chunk below
iris %>%
  mutate(Sepal.Area=Sepal.Length*Sepal.Width) %>%
  group_by( Species ) %>%
  summarize_if(is.numeric,mean)%>%
  ungroup() %>%
  pivot_longer( names_to="measure",values_to="value",cols=-Species ) %>%
  arrange(value )
```

```{r q2-solution}
## TODO: Re-write the code above following the tidyverse style guide
```

__q3__ Re-write according to the style guide

*Hint*: What do we do about long lines?

```{r q3-description}
iris %>%
  group_by(Species) %>%
  summarize(Sepal.Length = mean(Sepal.Length), Sepal.Width = mean(Sepal.Width), Petal.Length = mean(Petal.Length), Petal.Width = mean(Petal.Width))
```

```{r q3-task}
## TODO: Re-write the code above following the tidyverse style guide
```

<!-- include-exit-ticket -->
# Exit Ticket
<!-- -------------------------------------------------- -->

Once you have completed this exercise, make sure to fill out the **exit ticket survey**, [linked here](https://docs.google.com/forms/d/e/1FAIpQLSeuq2LFIwWcm05e8-JU84A3irdEL7JkXhMq5Xtoalib36LFHw/viewform?usp=pp_url&entry.693978880=e-comm00-style-assignment.Rmd).
